---
title: "ECLS-K Bootstrapping"
author: "Jess Helmer"
date: last-modified
toc: true
format: 
  html:
    code-fold: true
html-table-processing: none
---

::: panel-tabset
### Setup

```{r}
#| message: false
#| code-fold: show
library(tidyverse)
library(patchwork)
library(gt)

here::here("Scripts", "R") |> dir() |>
  walk(\(file) glue::glue("{here::here('Scripts', 'R')}/{file}") |> source())
```

### Reading
```{r}
#| code-fold: show
ecls <- readRDS(here::here("..", "Data", "ECLS-K", "ECLS-K.rds"))
```

```{r}
#| eval: false
ecls |> 
  names() |>
  str_extract("[a-zA-Z]_*\\d*")

ecls |> select(starts_with("T1")) |> names()

ecls |> select(starts_with("c2shape")) |>
  mutate(across(everything(), ~ recode_values(.x |> as.character(),
                                              "1: CORRECT" ~ 1,
                                              "2: INCORRECT" ~ 0,
                                              "-9: NOT ASCERTAINED" ~ NA,
                                              default = NA))) |>
  colMeans(na.rm = T)

ecls |> select(starts_with("T1"))
```
:::

Model: two-levels (students nested in schools) with a level-one predictor (student SES), level-two predictor (private vs. public school), and an interaction between them. The effect of SES has a varying slope over school. Outcome is student math score.

::: panel-tabset
### Traditional

::: math
\begin{aligned}

\text{MATH}_{ij} &= \beta_{0j} + \beta_{1j} \text{SES}_{ij} + r_{ij} \\
\beta_{0j} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} \\
\beta_{1j} &= \gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}

\end{aligned}
:::

::: math
\begin{aligned}
\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} + (\gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}) \text{SES}_{ij} + r_{ij} \\

\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + \gamma_{10} \text{SES}_{ij} + \gamma_{11} (\text{PRIVATE}_{1j} \times \text{SES}_{ij}) + u_{0j} + \text{SES}_{ij} u_{1j} + r_{ij}
\end{aligned}
:::

### Distributional

::: math
\begin{aligned}
\text{MATH}_{i} &\sim Normal(\mu_{i}, \sigma) \\

\mu_i &= \mu_{school[i]} + \beta_{SES_{school[i]}} SES_i \\

\mu_{school[i]} &= \alpha_{school[i]} + (\beta_{PRI} + \beta_{PRI \times SES} SES_i) PRI_{school[i]} \\

\begin{bmatrix}
 \alpha_{school[i]}\\
 \beta_{SES_{school[i]}}
\end{bmatrix} &\sim 

MVN \left(
\begin{bmatrix}
  \alpha \\
  \beta_{\text{SES}}
\end{bmatrix}, 
\textbf{S}
\right) \\ 

\textbf{S} &= 
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} 
\textbf{R}
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} \\[1em]

\alpha &\sim Normal(0, 2) \\ 
\beta_{\text{SES}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI} \times \text{SES}} &\sim Normal(0, 1) \\ 
(\sigma, \ \sigma_{\alpha}, \ \sigma_{\beta_{\text{SES}}}) &\sim Exp(1) \\
\textbf{R} &\sim LKJCorr(2)

\end{aligned}

:::

:::


### Full Data

Selecting columns with the outcome (math scores), level-one predictor (student SES), and level-two predictor (public vs. private school indicator). Removing any students with missing data on any of the predictors, and removing schools that have fewer than 10 students remaining.

```{r}
#| column: margin
ecls_dat <- ecls |>
  select(childid, s2_id, x12sesl, x2pubpri, x2mthetk5) |>
  mutate(private = recode_values(as.character(x2pubpri),
                                 "1: PUBLIC" ~ 0,
                                 "2: PRIVATE" ~ 1,
                                 "-1: NOT APPLICABLE" ~ NA,
                                 "-9: NOT ASCERTAINED" ~ NA),
         schoolid = s2_id,
         ses = x12sesl,
         mathscore = x2mthetk5,
         .keep = "unused") |>
    drop_na() |>
  # removing schools with less than 10 students
  filter_out(.by = schoolid,
             length(unique(childid)) < 10) 

list(ecls |> rename(schoolid = s2_id), ecls_dat) |>
  map(\(data) data |>
        select(schoolid, childid) |>
        summarize(schools = length(unique(schoolid)),
                  students = length(unique(childid)))) |>
  list_rbind() |>
  summarize(across(everything(), \(value)
                   range(value) |> 
                     reduce(`-`) |>
                     abs())) |>
  j_gt() |>
  tab_header("Units Removed")

```

Distributions of the outcome and predictors in the remaining data.

```{r}
#| fig-height: 3
ecls_dat |>
  select(-c(childid, schoolid)) |>
  imap(\(var, name) ecls_dat |> 
         ggplot(aes(x = var)) +
         {if (length(unique(var)) == 2) geom_bar() else geom_histogram(bins = 14)} +
         {if (length(unique(var)) == 2) scale_x_continuous(breaks = unique(var)) else NULL} +
         guides(x = guide_axis(name, cap = "both"),
                y = guide_axis(cap = "both")) +
         theme(aspect.ratio = 1)) |>
         wrap_plots()
```

Results from the model applied to the full dataset.

::: {style="font-size:70%"}
```{r}
#| layout-ncol: 2
m0 <- lme4::lmer(mathscore ~ 1 + (1 | schoolid),
                 dat = ecls_dat)
sjPlot::tab_model(m0,
                  title = "Unconditional")

m1 <- lme4::lmer(mathscore ~ ses * private + (ses | schoolid),
                 dat = ecls_dat)
sjPlot::tab_model(m1,
                  title = "Conditional")
```
:::


## Bootstrapping

```{r}
#| column: margin
params <- list(n_bootstraps = c(500),
               n_students = c(3, 10),
               n_schools = c(10, 30))

tibble(parameters = names(params),
       values = map(params, \(values) reduce(values, list))) |>
  gt() |>
  tab_style(cell_text(weight = "bold"),
            cells_column_labels()) |>
  cols_label_with(fn = str_to_title)

n_conditions <- params |> map(length) |> reduce(`*`)
```

Starting conditions: number of level-one units (students) within level-two units (schools). This set of parameters creates `r n_conditions` conditions.

```{r}
#| eval: false
#| code-fold: show

param_tbl <- do.call(crossing, params) |>
  mutate(condition_id = row_number(),
         .before = everything())

bs_dat <- param_tbl |>
  pmap(\(...) tibble(...) |>
         get_bootres())

saveRDS(bs_dat, here::here("Data", "2026-05-08_bs-dat.rds"))
```

```{r}
#| column: page
#| fig-height: 8
#| layout-ncol: 2
#| warning: false

bs_dat <- readRDS(here::here("Data", "2026-05-08_bs-dat.rds"))

bs_dat |>
  walk(\(bootres) {
    plt_dat <- make_plt_dat(bootres)
    
    pat <- make_plt_pattern(plt_dat)
    
    n_terms <- plt_dat |>
      select(n_terms) |>
      max()
    
    table_height_prop <- 1/4
    
    {
      (plt_dat |>
         pull(plots) |>
         unlist(recursive = F) |>
         append(wrap_table(make_warnings_tbl(bootres))) |>
         wrap_plots(design = pat,
                    axes = "collect",
                    heights = c(rep(((1 - table_height_prop) / n_terms), 
                                  times = n_terms),
                                table_height_prop))) |>
        cowplot::ggdraw() + 
        cowplot::draw_label(
          plot_annotation(bootres |> 
                            head(1) |>
                            select(starts_with("param")) |> 
                            rename_with(\(name) str_extract(name, "param_(.+)", group = 1)) |>
                            select(-condition_id) |>
                            imap_chr(\(value, name) glue::glue("{name}: {value}")) |> 
                            glue::glue_collapse(sep = ", ")),
          x = 0.5, y = 1, vjust = 1, fontface = "bold", size = 14)
    } |>
      print()
  })
```


#### Other Distributions by Condition

::: panel-tabset

### ICC

```{r}
#| message: false
#| warning: false
icc_dat <- bs_dat |>
  map(\(data) data |>
        select(model) |>
        mutate(
          icc = map_dbl(model, \(model) {
            
            icc <- performance::icc(model) |>
              pluck("ICC_adjusted") 
            
            ifelse(is.null(icc), NA, icc)  
          })
        ))


icc_dat |>
  map(\(data) data |>
        ggplot(aes(x = icc)) +
        geom_density(na.rm = T) +
        geom_text(data = data |>
                    mutate(icc_error = is.na(icc)) |>
                    summarize(percent_removed = mean(icc_error) * 100),
                  aes(label = glue::glue("{round(percent_removed, 2)}% ICCs errored"),
                      x = -Inf, y = Inf, vjust = 1, hjust = 0)) +
        scale_x_continuous("ICC", limits = c(0, 1), breaks = seq(0, 1, .2)) +
        scale_y_continuous(NULL, breaks = NULL) +
        guides(x = guide_axis(cap = T)) +
        theme(aspect.ratio = (1.618)^-1,
              axis.line.y = element_blank())) |>
  wrap_plots(ncol = 2, axes = "collect_x")
```

### $R^2$

```{r}
#| message: false
#| warning: false
#| results: hide
r2_dat <- bs_dat |>
  map(\(data) data |>
        select(model) |>
        mutate(
          r2s = map(model, \(model) {
            
            r2s <- performance::r2(model) 
            
            r2_conditional <- r2s$R2_conditional
            r2_marginal <- r2s$R2_marginal
          
            tribble(~ r2_type, ~ r2_estimate,
                    "conditional", ifelse(is.null(r2_conditional), NA, r2_conditional),
                    "marginal", ifelse(is.null(r2_marginal), NA, r2_marginal))
          })
        ) |>
            unnest(r2s))
  

r2_dat |>
  map(\(data) {
    error_dat <- data |>
      mutate(r2_error = is.na(r2_estimate)) |>
      summarize(.by = r2_type,
                percent_removed = mean(r2_error) * 100) |>
      mutate(string = glue::glue("{round(percent_removed, 2)}% {r2_type} R^2s errored"))

    data |>
      ggplot(aes(x = r2_estimate, color = r2_type)) +
      geom_density(na.rm = T) +
      geom_text(data = error_dat,
                aes(label = string,
                    x = -Inf, y = Inf, vjust = c(1, 2.3), hjust = 0)) +
      scale_x_continuous("R^2", limits = c(0, 1), breaks = seq(0, 1, .2)) +
      scale_y_continuous(NULL, breaks = NULL) +
      guides(x = guide_axis(cap = T),
             color = guide_none()) +
      theme(aspect.ratio = (1.618)^-1,
            axis.line.y = element_blank(),
            axis.title.x = ggtext::element_markdown())
    }) |>
 wrap_plots(ncol = 2, axes = "collect_x")
```
:::

## Generated Data

Generating data from model estimates of one bootstrap hit.

```{r}
# bs_dat |>
#   pluck(1) |>
#   unnest(tidy) |>
#   filter(term == "ses") |>
#   filter(estimate > quantile(estimate, .97)) |>
#   arrange(desc(estimate)) # didn't estimate intercept

# bs_dat |>
#   pluck(1) |>
#   unnest(tidy) |>
#   filter(term == "sd__(Intercept)") |>
#   filter(estimate > quantile(estimate, .97)) |>
#   arrange(desc(estimate))

data_gen_params <- bs_dat |>
  pluck(1) |>
  filter(id == "331") |>
  unnest(tidy) |>
  select(param_n_bootstraps, param_n_schools, param_n_students, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)

data_gen_params |>
  gt() |>
  fmt_number()

data_gen_vcov <- matrix(c(data_gen_params$`sd__(Intercept)`,
         0,
         0,
         data_gen_params$`sd__ses`),
       ncol = 2, byrow = T) %*% 
  matrix(c(1,
           data_gen_params$`cor__(Intercept).ses`,
           data_gen_params$`cor__(Intercept).ses`,
           1),
       ncol = 2, byrow = T) %*%
  matrix(c(data_gen_params$`sd__(Intercept)`,
           0,
           0,
           data_gen_params$`sd__ses`),
       ncol = 2, byrow = T)
```

```{r}
gen_data <- function(data_gen_params) {
  tibble(schoolid = seq(1, data_gen_params$param_n_schools),
         n_students = data_gen_params$param_n_students,
         private = rbinom(data_gen_params$param_n_schools, 1, .3),
         beta_ses = data_gen_params$ses,
         beta_private = data_gen_params$private,
         beta_private_by_ses = data_gen_params$`ses:private`) |>
    bind_cols(varying_effects = MASS::mvrnorm(data_gen_params$param_n_schools, 
                                              mu = c(data_gen_params$`(Intercept)`, data_gen_params$ses), 
                                              Sigma = data_gen_vcov) |>
                as_tibble() |>
                set_names(c("alpha_school", "beta_ses_school"))) |>
    uncount(n_students) |>
    mutate(studentid = row_number(),
           .after = schoolid) |>
    mutate(ses = rnorm(data_gen_params$param_n_schools * data_gen_params$param_n_students),
           private_by_ses = private * ses,
           mu_school = alpha_school + 
             beta_private * private +
             beta_private_by_ses * private_by_ses,
           mu = mu_school + beta_ses * ses,
           mathscore = rnorm(data_gen_params$param_n_schools * data_gen_params$param_n_students,
                        mean = mu, sd = data_gen_params$sd__Observation)) |>
    nest(gen_params = c(starts_with("beta"), starts_with("alpha"), starts_with("mu")))
}


```

```{r}
#| warning: false
#| message: false
frm <- mathscore ~ ses * private + (ses | schoolid)

bs_gen_dat <- tibble(iter = seq(1, data_gen_params$param_n_bootstraps),
                     strap = map(iter, \(iter) gen_data(data_gen_params))) |>
  mutate(res = map(strap, 
                   safely(\(strap) lme4::lmer(frm,
                                              data = strap),
                          otherwise = NA_real_)),
         model = map(res, "result"),
         error = map_chr(res, \(res) pluck(res, "error", "message", .default = NA)),
         tidy = imap(model, \(model, idx) model |>
                       broom.mixed::tidy() |>
                       mutate(iter = idx)),
         opt_warnings = map_chr(model, get_warnings),
         lme4_warnings = map_chr(model, get_lme4_warnings)) |>
  bind_cols(data_gen_params)

```

```{r}
#| column: page
#| fig-height: 8
#| warning: false

list(bs_gen_dat) |>
  walk(\(bootres) {
    plt_dat <- make_plt_dat(bootres)
    
    pat <- make_plt_pattern(plt_dat)
    
    n_terms <- plt_dat |>
      select(n_terms) |>
      max()
    
    table_height_prop <- 1/4
    
    {
      (plt_dat |>
         pull(plots) |>
         unlist(recursive = F) |>
         append(wrap_table(make_warnings_tbl(bootres))) |>
         wrap_plots(design = pat,
                    axes = "collect",
                    heights = c(rep(((1 - table_height_prop) / n_terms), 
                                  times = n_terms),
                                table_height_prop))) |>
        cowplot::ggdraw() + 
        cowplot::draw_label(
          plot_annotation("Generated Data Bootstrap"),
          x = 0.5, y = 1, vjust = 1, fontface = "bold", size = 14)
    } |>
      print()
  })
```

#### Other Distributions by Condition

::: panel-tabset

### ICC

```{r}
#| message: false
#| warning: false
icc_dat <- list(bs_gen_dat) |>
  map(\(data) data |>
        select(model) |>
        mutate(
          icc = map_dbl(model, \(model) {
            
            icc <- performance::icc(model) |>
              pluck("ICC_adjusted") 
            
            ifelse(is.null(icc), NA, icc)  
          })
        ))


icc_dat |>
  map(\(data) data |>
        ggplot(aes(x = icc)) +
        geom_density(na.rm = T) +
        geom_text(data = data |>
                    mutate(icc_error = is.na(icc)) |>
                    summarize(percent_removed = mean(icc_error) * 100),
                  aes(label = glue::glue("{round(percent_removed, 2)}% ICCs errored"),
                      x = -Inf, y = Inf, vjust = 1, hjust = 0)) +
        scale_x_continuous("ICC", limits = c(0, 1), breaks = seq(0, 1, .2)) +
        scale_y_continuous(NULL, breaks = NULL) +
        guides(x = guide_axis(cap = T)) +
        theme(aspect.ratio = (1.618)^-1,
              axis.line.y = element_blank())) |>
  wrap_plots(ncol = 2, axes = "collect_x")
```

### $R^2$

```{r}
#| message: false
#| warning: false
#| results: hide
r2_dat <- list(bs_gen_dat) |>
  map(\(data) data |>
        select(model) |>
        mutate(
          r2s = map(model, \(model) {
            
            r2s <- performance::r2(model) 
            
            r2_conditional <- r2s$R2_conditional
            r2_marginal <- r2s$R2_marginal
          
            tribble(~ r2_type, ~ r2_estimate,
                    "conditional", ifelse(is.null(r2_conditional), NA, r2_conditional),
                    "marginal", ifelse(is.null(r2_marginal), NA, r2_marginal))
          })
        ) |>
            unnest(r2s))
  

r2_dat |>
  map(\(data) {
    error_dat <- data |>
      mutate(r2_error = is.na(r2_estimate)) |>
      summarize(.by = r2_type,
                percent_removed = mean(r2_error) * 100) |>
      mutate(string = glue::glue("{round(percent_removed, 2)}% {r2_type} R^2s errored"))

    data |>
      ggplot(aes(x = r2_estimate, color = r2_type)) +
      geom_density(na.rm = T) +
      geom_text(data = error_dat,
                aes(label = string,
                    x = -Inf, y = Inf, vjust = c(1, 2.3), hjust = 0)) +
      scale_x_continuous("R^2", limits = c(0, 1), breaks = seq(0, 1, .2)) +
      scale_y_continuous(NULL, breaks = NULL) +
      guides(x = guide_axis(cap = T),
             color = guide_none()) +
      theme(aspect.ratio = (1.618)^-1,
            axis.line.y = element_blank(),
            axis.title.x = ggtext::element_markdown())
    }) |>
 wrap_plots(ncol = 2, axes = "collect_x")
```

## Archive

<!-- ```{r} -->
<!-- bootstr <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") -->

<!-- t1 <- Sys.time() -->
<!-- bootres <- bootstr |> -->
<!--   mutate(model = map(strap,  -->
<!--                      \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                          data = strap)), -->
<!--          tidy = map(model, broom.mixed::tidy), -->
<!--          opt_warnings = map_chr(model, get_warnings), -->
<!--          lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- t2 <- Sys.time() -->

<!-- get_bootres <- function(bootstrapped_dat) { -->
<!--   frm <- mathscore ~ ses * private + (ses | schoolid) -->

<!--   bootstrapped_dat |> -->
<!--     mutate(model = map(strap,  -->
<!--                        \(strap) lme4::lmer(frm, -->
<!--                                            data = strap)), -->
<!--            tidy = map(model, broom.mixed::tidy), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- } -->

<!-- t3 <- Sys.time() -->
<!-- get_bootres(bootstr) -->
<!-- t4 <- Sys.time() -->

<!-- (t2 - t1) -->
<!-- (t4 - t3) -->

<!-- bootest <- bootres |> -->
<!--   # giving each `tidy` an iteration id -->
<!--   mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) |> -->
<!--   list_rbind() |> -->
<!--   select(group, term, estimate, iter) -->
<!-- ``` -->



<!-- ```{r} -->
<!-- bootstr <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") -->

<!-- t1 <- Sys.time() -->
<!-- bootres <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") |> -->
<!--   mutate(model = map(strap,  -->
<!--                      \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                          data = strap)), -->
<!--          tidy = map(model, broom.mixed::tidy), -->
<!--          opt_warnings = map_chr(model, get_warnings), -->
<!--          lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- t2 <- Sys.time() -->

<!-- get_bootres <- function(n_bootstraps) { -->
<!--   frm <- mathscore ~ ses * private + (ses | schoolid) -->

<!--   ecls_dat |> -->
<!--     # should this take into account the clustering more? -->
<!--     modelr::bootstrap(n_bootstraps, id = "id") |> -->
<!--     mutate(model = map(strap,  -->
<!--                        \(strap) lme4::lmer(frm, -->
<!--                                            data = strap)), -->
<!--            tidy = imap(model, \(model, idx) model |> -->
<!--                         broom.mixed::tidy() |> -->
<!--                         mutate(iter = idx)), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- } -->

<!-- t3 <- Sys.time() -->
<!-- get_bootres(n_bootstraps) -->
<!-- t4 <- Sys.time() -->

<!-- (t2 - t1) -->
<!-- (t4 - t3) -->

<!-- b <- get_bootres(10) -->

<!-- b |> mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) -->

<!-- bootest <- bootres |> -->
<!--   # giving each `tidy` an iteration id -->
<!--   mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) |> -->
<!--   list_rbind() |> -->
<!--   select(group, term, estimate, iter) -->
<!-- ``` -->




<!-- ```{r} -->

<!-- plt_dat <- tibble(term = terms) |> -->
<!--   mutate(plot_terms = imap(term, \(term, idx) tibble(xterm = term, -->
<!--                                                      yterm = head(terms, idx))), -->
<!--          n_terms = map_int(plot_terms, \(plot_terms) nrow(plot_terms)), -->
<!--          n_prev_terms = map_int(n_terms, \(n_terms) seq(n_terms - 1, 0) |> sum()), -->
<!--          # pat only worked as a way to setup the patchwork when length(terms) < 7 -->
<!--          pat = map2_chr(n_terms, n_prev_terms, -->
<!--                         \(n_terms, n_prev_terms) paste0(LETTERS[seq(n_prev_terms + 1, length.out = n_terms)] |>  -->
<!--                                                           paste(collapse = ""), -->
<!--                                             rep("#", times = length(terms) - n_terms) |> paste(collapse = "")))) |> -->
<!--   mutate(plots = map(plot_terms, -->
<!--                           \(plot_terms) plot_terms |> -->
<!--                             mutate(plot = map2(xterm, yterm, -->
<!--                                                \(xterm, yterm) { -->

<!--                                                  df <- bootest |> -->
<!--                                                    filter(term %in% c(xterm, yterm)) |> -->
<!--                                                    select(term, estimate, iter) |> -->
<!--                                                    pivot_wider(names_from = term, values_from = estimate) -->

<!--                                                  mapping <- if (xterm == yterm) { -->
<!--                                                    do.call(aes, list(x = as.name(xterm))) -->
<!--                                                  } else { -->
<!--                                                    do.call(aes, list(y = as.name(xterm), x = as.name(yterm))) -->
<!--                                                  } -->
<!--                                                  geom <- if (xterm == yterm) geom_density() else geom_point() -->

<!--                                                  ggplot(df, mapping) +  -->
<!--                                                    geom + -->
<!--                                                    {if (xterm == yterm) labs(y = NULL) else NULL} + -->
<!--                                                    scale_x_continuous(breaks = NULL) + -->
<!--                                                    scale_y_continuous(breaks = NULL) + -->
<!--                                                    theme_classic() -->
<!--                                                }))  |> pluck("plot"))) -->


<!-- ``` -->
```{r}
#| eval: false



# bootres <- get_bootres(10)
# 
# plt_dat <- make_plt_dat(bootres)
# 
# pat <- make_plt_pattern(plt_dat)
# 
# plt_dat |>
#     pull(plots) |>
#     unlist(recursive = F) |>
#     wrap_plots(design = pat,
#                axes = "collect")

list(n_bootstraps = c(10, 20),
     n_students = c(3, 10),
     n_schools = c(5, 20)) |>
  do.call(crossing, args = _) |>
  mutate(condition_id = row_number()) |>
  nest(params = -condition_id) |>
  pull(params) |>
  map(\(params) {
    print(params)
    
    params |>
      pivot_longer(everything(),
                   names_to = "param",
                   values_to = "value") |>
      pmap(\(param, value) assign(param, value))
    
    glue::glue("{param}: {value}")
  })

# bs_dat <- do.call(crossing, params) |>
#   mutate(condition_id = row_number()) |>
#   pmap(\(...) {
#     list2env(list(...), envir = environment())
#     glue::glue("condition {condition_id}: n_bootstraps={n_bootstraps}, n_students={n_students}, n_schools={n_schools}")
#     
#     get_bootres(n_bootstraps, n_students, n_schools) |>
#       mutate(condition_str = glue::glue("condition {condition_id}: n_bootstraps={n_bootstraps}, n_students={n_students},  n_schools={n_schools}"))
#   })



bs_dat |>
  head(2) |>
  map(\(bootres) {
    plt_dat <- 
    
    make_plt_pattern(plt_dat)
    })

make_plt_dat(bres) |>
    get_table_row_location

p1 <- ggplot(mtcars) + geom_point(aes(mpg, disp)) + theme_classic()
p2 <- ggplot(mtcars) + geom_boxplot(aes(gear, disp, group = gear)) + theme_classic()
p3 <- ggplot(mtcars) + geom_bar(aes(gear)) + facet_wrap(~cyl) + theme_classic()


design <- "
  AB
  AC
"

(p1 + p2 + p3) +
  plot_layout(design = design, heights = c(3, 1), axes = "collect") &
  theme_classic()
```

<!-- ### Bootstrapped Data -->

<!-- ```{r} -->
<!-- m1_bs <- function(n_students) { -->
<!--   bootstr <- ecls_dat |> -->
<!--     filter(.by = schoolid, -->
<!--            childid %in% sample(childid, n_students)) |> -->
<!--     modelr::bootstrap(n_bootstraps, id = "studentid") -->

<!--   bootres <- bootstr |> -->
<!--     mutate(model = map(strap, -->
<!--                        \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                            dat = strap)), -->
<!--            tidy = map(model, broom.mixed::tidy), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!--   #  -->
<!--   # # n_students <- bootres |> -->
<!--   # #   pull(n_students) |>  -->
<!--   # #   first() -->
<!--   #  -->
<!--   bootest <- bootres |> -->
<!--     # giving each `tidy` an iteration id -->
<!--     mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--     pull(tidy) |> -->
<!--     list_rbind() |> -->
<!--     select(group, term, estimate, iter) -->
<!--   #  -->
<!--   terms <- bootest |> pull(term) |> unique() -->

<!--   plt_dat <- tibble(term = terms) |> -->
<!--     mutate(plot_terms = imap(term, \(term, idx) tibble(xterm = term, -->
<!--                                                        yterm = head(terms, idx))), -->
<!--            n_terms = map_int(plot_terms, \(plot_terms) nrow(plot_terms)), -->
<!--            n_prev_terms = map_int(n_terms, \(n_terms) seq(n_terms - 1, 0) |> sum()), -->
<!--            pat = map2_chr(n_terms, n_prev_terms, -->
<!--                           \(n_terms, n_prev_terms) paste0(LETTERS[seq(n_prev_terms + 1, length.out = n_terms)] |> -->
<!--                                                             paste(collapse = ""), -->
<!--                                                           rep("#", times = length(terms) - n_terms) |> paste(collapse = "")))) |> -->
<!--     mutate(plots = map(plot_terms, -->
<!--                        \(plot_terms) plot_terms |> -->
<!--                          mutate(plot = map2(xterm, yterm, -->
<!--                                             \(xterm, yterm) { -->

<!--                                               df <- bootest |> -->
<!--                                                 filter(term %in% c(xterm, yterm)) |> -->
<!--                                                 select(term, estimate, iter) |> -->
<!--                                                 pivot_wider(names_from = term, values_from = estimate) -->

<!--                                               mapping <- if (xterm == yterm) { -->
<!--                                                 do.call(aes, list(x = as.name(xterm))) -->
<!--                                               } else { -->
<!--                                                 do.call(aes, list(y = as.name(xterm), x = as.name(yterm))) -->
<!--                                               } -->
<!--                                               geom <- if (xterm == yterm) geom_density() else geom_point() -->

<!--                                               ggplot(df, mapping) + -->
<!--                                                 geom + -->
<!--                                                 {if (xterm == yterm) labs(y = NULL) else NULL} + -->
<!--                                                 scale_x_continuous(breaks = NULL) + -->
<!--                                                 scale_y_continuous(breaks = NULL) + -->
<!--                                                 theme_classic() -->
<!--                                             }))  |> pluck("plot"))) -->


<!--   pat <- plt_dat |> -->
<!--     select(n_terms, n_prev_terms) |> -->
<!--     mutate(areas = map(n_terms, -->
<!--                        \(n_terms) seq(1, n_terms) |> -->
<!--                          map2(n_terms, \(y, x) c(x, y)) -->
<!--     )) |> -->
<!--     pull(areas) |> -->
<!--     list_flatten() |> -->
<!--     map(\(a) area(t = a[1], l = a[2], b = a[1], r = a[2])) |> -->
<!--     reduce(c) -->


<!--   plt_dat |> -->
<!--     pull(plots) |> -->
<!--     unlist(recursive = F) |> -->
<!--     wrap_plots(design = pat, -->
<!--                axes = "collect") + -->
<!--     plot_annotation(title = glue::glue("Students per Classroom: {n_students}")) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- list(3, 10) |> -->
<!--   map(\(n_students) m1_bs(n_students)) -->


<!-- bootres <- list(3, 10) |> -->
<!--   map(\(n_students) m1_bs(n_students)) -->

<!-- m1_bs(3) -->

<!-- bootres |> -->
<!--   map(m1_bs_plt) -->

<!-- bootres |> -->
<!--   map(\(bootres) bootres |> -->
<!--         summarize(opt_warnings = list(unique(opt_warnings)))) -->
<!-- ``` -->
















