---
title: "ECLS-K Bootstrapping"
author: "Jess Helmer"
date: last-modified
format: 
  html:
    code-fold: true
    toc: true
    toc-location: left
toc-depth: 4
html-table-processing: none
---

```{r reading}
#| message: false
library(tidyverse)
library(targets)
library(patchwork)
library(ggtext)
library(gt)

tar_source(here::here("Scripts", "R"))

c(
  ecls_dat, param_set, params,
  full_data_models
  #examples_params, examples_spaghetti_plts, examples_icc_plt, examples_r2_plt
  ) |>
  tar_load(store = here::here("_targets"))
```


Model: two-levels (students nested in schools) with a level-one predictor (student SES), level-two predictor (private vs. public school), and an interaction between them. The effect of SES has a varying slope over school. Outcome is student math score.

::: panel-tabset
### Traditional

::: math
\begin{aligned}

\text{MATH}_{ij} &= \beta_{0j} + \beta_{1j} \text{SES}_{ij} + r_{ij} \\
\beta_{0j} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} \\
\beta_{1j} &= \gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}

\end{aligned}
:::

::: math
\begin{aligned}
\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} + (\gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}) \text{SES}_{ij} + r_{ij} \\

\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + \gamma_{10} \text{SES}_{ij} + \gamma_{11} (\text{PRIVATE}_{1j} \times \text{SES}_{ij}) + u_{0j} + \text{SES}_{ij} u_{1j} + r_{ij}
\end{aligned}
:::

### Distributional

::: math
\begin{aligned}
\text{MATH}_{i} &\sim Normal(\mu_{i}, \sigma) \\

\mu_i &= \mu_{school[i]} + \beta_{SES_{school[i]}} SES_i \\

\mu_{school[i]} &= \alpha_{school[i]} + (\beta_{PRI} + \beta_{PRI \times SES} SES_i) PRI_{school[i]} \\

\begin{bmatrix}
 \alpha_{school[i]}\\
 \beta_{SES_{school[i]}}
\end{bmatrix} &\sim 

MVN \left(
\begin{bmatrix}
  \alpha \\
  \beta_{\text{SES}}
\end{bmatrix}, 
\textbf{S}
\right) \\ 

\textbf{S} &= 
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} 
\textbf{R}
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} \\[1em]

\alpha &\sim Normal(0, 2) \\ 
\beta_{\text{SES}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI} \times \text{SES}} &\sim Normal(0, 1) \\ 
(\sigma, \ \sigma_{\alpha}, \ \sigma_{\beta_{\text{SES}}}) &\sim Exp(1) \\
\textbf{R} &\sim LKJCorr(2)

\end{aligned}

:::

:::


## Full Data

Selecting columns with the outcome (math scores), level-one predictor (student SES), and level-two predictor (public vs. private school indicator). Removing any students with missing data on any of the predictors, and removing schools that have fewer than 10 students remaining.

```{r}
#| column: margin
# list(ecls |> rename(schoolid = s2_id), ecls_dat) |>
#   map(\(data) data |>
#         select(schoolid, childid) |>
#         summarize(schools = length(unique(schoolid)),
#                   students = length(unique(childid)))) |>
#   list_rbind() |>
#   summarize(across(everything(), \(value)
#                    range(value) |> 
#                      reduce(`-`) |>
#                      abs())) |>
#   j_gt() |>
#   tab_header("Units Removed")

```

```{r ecls_info}
#| layout-ncol: 2
ecls_dat |>
  select(schoolid, childid) |>
  summarize(schools = length(unique(schoolid)),
            students = length(unique(childid))) |>
  j_gt() |>
  tab_header("Total Units Remaining")

ecls_dat |>
  select(schoolid, childid) |>
  summarize(.by = schoolid,
            n_students = length(unique(childid))) |>
  ggplot(aes(x = n_students, y = after_stat(density))) +
  geom_histogram(binwidth = 1, alpha = .8) +
  scale_y_continuous("Percent", labels = scales::label_percent()) +
  guides(y = guide_axis(cap = T),
         x = guide_axis("Students Per School", cap = T)) +
  theme(geom = element_geom(ink = "skyblue3", color = "skyblue3"))
```


Distributions of the outcome and predictors in the remaining data.

```{r ecls_distributions}
#| fig-height: 3
ecls_dat |>
  select(-c(childid, schoolid)) |>
  imap(\(var, name) ecls_dat |> 
         ggplot(aes(x = var)) +
         {if (length(unique(var)) == 2) geom_bar() else geom_histogram(bins = 14)} +
         {if (length(unique(var)) == 2) scale_x_continuous(breaks = unique(var)) else NULL} +
         guides(x = guide_axis(name, cap = "both"),
                y = guide_axis(cap = "both")) +
         theme(aspect.ratio = 1)) |>
         wrap_plots()
```

Results from the model applied to the full dataset.

::: {style="font-size:70%"}
```{r}
#| layout-ncol: 3
#| column: page
full_data_models[1, "full_res"][[1]] |> sjPlot::tab_model(title = "Unconditional")

full_data_models[2, "full_res"][[1]] |> sjPlot::tab_model(title = "Level-One Predictor")

full_data_models[3, "full_res"][[1]] |> sjPlot::tab_model(title = "Level-One and Level-Two Predictor")

full_data_models[4, "full_res"][[1]] |> sjPlot::tab_model(title = "Cross-Level Interaction")

full_data_models[5, "full_res"][[1]] |> sjPlot::tab_model(title = "Full")

```
:::

### Bootstrapping the Full Data


## Bootstrapping

```{r param_tbl}
#| column: margin


param_set_no_model <- param_set |>
  list_modify("model_string" = rlang::zap())

tibble(parameters = names(param_set_no_model),
       values = map(param_set_no_model, \(values) reduce(values, list))) |>
  gt() |>
  tab_style(cell_text(weight = "bold"),
            cells_column_labels()) |>
  cols_label_with(fn = str_to_title)

n_conditions <- param_set_no_model |> map(length) |> reduce(`*`)

n_within_model_conditions <- params |>
  count(model_string) |>
  pluck("n", 1)

condition_plt_files <- targets::tar_read(condition_plt_files, 
                                         store = here::here("_targets")) |>
  unlist()

c("both", "cluster", "individual") |>
  walk(\(bstype) {
    nm <- as.character(glue::glue("condition_plt_files_bstype_{bstype}"))
    assign(nm, condition_plt_files[which(str_detect(condition_plt_files, glue::glue("bstype_{bstype}")))], .GlobalEnv)
  })

icc_plt_files <- targets::tar_read(icc_plt_files, 
                                   store = here::here("_targets")) |>
  unlist()

c("both", "cluster", "individual") |>
  walk(\(bstype) {
    nm <- as.character(glue::glue("icc_plt_files_bstype_{bstype}"))
    assign(nm, icc_plt_files[which(str_detect(icc_plt_files, glue::glue("bstype_{bstype}")))], .GlobalEnv)
  })

r2_plt_files <- targets::tar_read(r2_plt_files, 
                                   store = here::here("_targets")) |>
  unlist()

c("both", "cluster", "individual") |>
  walk(\(bstype) {
    nm <- as.character(glue::glue("r2_plt_files_bstype_{bstype}"))
    assign(nm, r2_plt_files[which(str_detect(r2_plt_files, glue::glue("bstype_{bstype}")))], .GlobalEnv)
  })
```

```{r}
tar_read(params) |>
  select(btwn_condition_id, n_students, n_schools, model_string,
         centered, bootstrap_type, full_data) |>
  unique()
```


Starting conditions: number of level-one units (students) within level-two units (schools). This set of parameters creates `r n_conditions` conditions per model.

### Bootstrapping Type: Both

First randomly sampling `n_schools` schools, then randomly sampling `n_students` students from within those schools. 

```{r}
condition_plt_files <- condition_plt_files_bstype_both
icc_plt_files <- icc_plt_files_bstype_both
r2_plt_files <- r2_plt_files_bstype_both

model_ids <- condition_plt_files |> 
  str_extract("model_(\\d)", group = 1) |> 
  unique()

model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))
```

:::: panel-tabset

## Unconditional Model

::: panel-tabset

### Non-Centered
```{r model_1_not_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_1_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[1]]] |>
  knitr::include_graphics()
```
:::

## Level-One Predictor Model

::: panel-tabset

### Non-Centered
```{r model_2_not_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_2_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

:::

## Level-One and Level-Two Predictor Model

::: panel-tabset

### Non-Centered
```{r model_3_not_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_3_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

:::

## Cross-Level Interaction Model

::: panel-tabset

### Non-Centered
```{r model_4_not_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_4_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

:::

## Full Model

::: panel-tabset

### Non-Centered
```{r model_5_not_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_5_centered_condition_plts_both}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

:::
::::

#### Other Distributions

All of these distributions are from the non-centered versions of the data subsets.

:::: panel-tabset

### ICC

::: panel-tabset
### Unconditional Model
```{r icc_plt_1_both}
icc_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

icc_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

icc_plt_files[icc_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Level-One Predictor Model
```{r icc_plt_2_both}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r icc_plt_3_both}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r icc_plt_4_both}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r icc_plt_5_both}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

### $R^2$ 

::: panel-tabset
### Unconditional Model
```{r r2_plt_1_both}
r2_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(r2_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

r2_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

r2_plt_files[r2_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### One-Predictor Model
```{r r2_plt_2_both}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r r2_plt_3_both}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r r2_plt_4_both}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r r2_plt_5_both}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

::::


### Bootstrapping Type: Cluster

Randomly sampling `n_schools` schools.

```{r}
condition_plt_files <- condition_plt_files_bstype_cluster
icc_plt_files <- icc_plt_files_bstype_cluster
r2_plt_files <- r2_plt_files_bstype_cluster

model_ids <- condition_plt_files |> 
  str_extract("model_(\\d)", group = 1) |> 
  unique()

model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))
```

:::: panel-tabset

## Unconditional Model

::: panel-tabset

### Non-Centered
```{r model_1_not_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_1_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[1]]] |>
  knitr::include_graphics()
```
:::

## Level-One Predictor Model

::: panel-tabset

### Non-Centered
```{r model_2_not_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_2_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

:::

## Level-One and Level-Two Predictor Model

::: panel-tabset

### Non-Centered
```{r model_3_not_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_3_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

:::

## Cross-Level Interaction Model

::: panel-tabset

### Non-Centered
```{r model_4_not_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_4_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

:::

## Full Model

::: panel-tabset

### Non-Centered
```{r model_5_not_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_5_centered_condition_plts_cluster}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

:::
::::

#### Other Distributions

All of these distributions are from the non-centered versions of the data subsets.

:::: panel-tabset

### ICC

::: panel-tabset
### Unconditional Model
```{r icc_plt_1_cluster}
icc_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

icc_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

icc_plt_files[icc_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Level-One Predictor Model
```{r icc_plt_2_cluster}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r icc_plt_3_cluster}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r icc_plt_4_cluster}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r icc_plt_5_cluster}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

### $R^2$ 

::: panel-tabset
### Unconditional Model
```{r r2_plt_1_cluster}
r2_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(r2_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

r2_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

r2_plt_files[r2_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### One-Predictor Model
```{r r2_plt_2_cluster}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r r2_plt_3_cluster}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r r2_plt_4_cluster}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r r2_plt_5_cluster}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

::::


### Bootstrapping Type: Individual

Randomly sampling `n_schools * n_students` students.

```{r}
condition_plt_files <- condition_plt_files_bstype_individual
icc_plt_files <- icc_plt_files_bstype_individual
r2_plt_files <- r2_plt_files_bstype_individual

model_ids <- condition_plt_files |> 
  str_extract("model_(\\d)", group = 1) |> 
  unique()

model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(condition_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))
```

:::: panel-tabset

## Unconditional Model

::: panel-tabset

### Non-Centered
```{r model_1_not_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_1_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[1]]] |>
  knitr::include_graphics()
```
:::

## Level-One Predictor Model

::: panel-tabset

### Non-Centered
```{r model_2_not_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_2_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

:::

## Level-One and Level-Two Predictor Model

::: panel-tabset

### Non-Centered
```{r model_3_not_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_3_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

:::

## Cross-Level Interaction Model

::: panel-tabset

### Non-Centered
```{r model_4_not_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_4_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

:::

## Full Model

::: panel-tabset

### Non-Centered
```{r model_5_not_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

### Centered
```{r model_5_centered_condition_plts_individual}
#| column: page
#| layout-ncol: 2
#| warning: false

condition_plt_files[model_id_centered_idxs[[5]]] |>
  knitr::include_graphics()
```

:::
::::

#### Other Distributions

All of these distributions are from the non-centered versions of the data subsets.

:::: panel-tabset

### ICC

::: panel-tabset
### Unconditional Model
```{r icc_plt_1_individual}
icc_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

icc_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

icc_plt_files[icc_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### Level-One Predictor Model
```{r icc_plt_2_individual}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r icc_plt_3_individual}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r icc_plt_4_individual}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r icc_plt_5_individual}
icc_plt_files[icc_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

### $R^2$ 

::: panel-tabset
### Unconditional Model
```{r r2_plt_1_individual}
r2_plt_model_id_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(r2_plt_files, glue::glue("model_{model_id}_centered_TRUE"))
                     ))

r2_plt_model_id_not_centered_idxs <- map(model_ids, 
                     \(model_id) which(
                       str_detect(icc_plt_files, glue::glue("model_{model_id}_centered_FALSE"))
                     ))

r2_plt_files[r2_plt_model_id_not_centered_idxs[[1]]] |>
  knitr::include_graphics()
```

### One-Predictor Model
```{r r2_plt_2_individual}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[2]]] |>
  knitr::include_graphics()
```

### Level-One and Level-Two Predictor Model
```{r r2_plt_3_individual}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[3]]] |>
  knitr::include_graphics()
```

### Cross-Level Interaction Model
```{r r2_plt_4_individual}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[4]]] |>
  knitr::include_graphics()
```

### Full Model
```{r r2_plt_5_individual}
r2_plt_files[r2_plt_model_id_not_centered_idxs[[5]]] |>
  knitr::include_graphics()
```
:::

::::







