---
title: "ECLS-K Bootstrapping"
author: "Jess Helmer"
date: last-modified
toc: true
format: 
  html:
    code-fold: true
html-table-processing: none
---

::: panel-tabset
### Setup

```{r reading}
#| message: false
#| code-fold: show
library(tidyverse)
library(targets)
library(patchwork)
library(ggtext)
library(gt)

tar_source(here::here("Scripts", "R"))

c(ecls_dat, param_set, icc_plt, r2_plt, 
  examples_params, examples_spaghetti_plts, examples_icc_plt, examples_r2_plt) |>
  tar_load(store = here::here("_targets"))
```

### Reading

:::

Model: two-levels (students nested in schools) with a level-one predictor (student SES), level-two predictor (private vs. public school), and an interaction between them. The effect of SES has a varying slope over school. Outcome is student math score.

::: panel-tabset
### Traditional

::: math
\begin{aligned}

\text{MATH}_{ij} &= \beta_{0j} + \beta_{1j} \text{SES}_{ij} + r_{ij} \\
\beta_{0j} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} \\
\beta_{1j} &= \gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}

\end{aligned}
:::

::: math
\begin{aligned}
\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + u_{0j} + (\gamma_{10} + \gamma_{11} \text{PRIVATE}_{1j} + u_{1j}) \text{SES}_{ij} + r_{ij} \\

\text{MATH}_{ij} &= \gamma_{00} + \gamma_{01} \text{PRIVATE}_{0j} + \gamma_{10} \text{SES}_{ij} + \gamma_{11} (\text{PRIVATE}_{1j} \times \text{SES}_{ij}) + u_{0j} + \text{SES}_{ij} u_{1j} + r_{ij}
\end{aligned}
:::

### Distributional

::: math
\begin{aligned}
\text{MATH}_{i} &\sim Normal(\mu_{i}, \sigma) \\

\mu_i &= \mu_{school[i]} + \beta_{SES_{school[i]}} SES_i \\

\mu_{school[i]} &= \alpha_{school[i]} + (\beta_{PRI} + \beta_{PRI \times SES} SES_i) PRI_{school[i]} \\

\begin{bmatrix}
 \alpha_{school[i]}\\
 \beta_{SES_{school[i]}}
\end{bmatrix} &\sim 

MVN \left(
\begin{bmatrix}
  \alpha \\
  \beta_{\text{SES}}
\end{bmatrix}, 
\textbf{S}
\right) \\ 

\textbf{S} &= 
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} 
\textbf{R}
\begin{bmatrix}
  \sigma_{\alpha} & 0 \\
  0 & \sigma_{\beta_{\text{SES}}}
\end{bmatrix} \\[1em]

\alpha &\sim Normal(0, 2) \\ 
\beta_{\text{SES}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI}} &\sim Normal(0, 1) \\ 
\beta_{\text{PRI} \times \text{SES}} &\sim Normal(0, 1) \\ 
(\sigma, \ \sigma_{\alpha}, \ \sigma_{\beta_{\text{SES}}}) &\sim Exp(1) \\
\textbf{R} &\sim LKJCorr(2)

\end{aligned}

:::

:::


### Full Data

Selecting columns with the outcome (math scores), level-one predictor (student SES), and level-two predictor (public vs. private school indicator). Removing any students with missing data on any of the predictors, and removing schools that have fewer than 10 students remaining.

```{r}
#| column: margin
# list(ecls |> rename(schoolid = s2_id), ecls_dat) |>
#   map(\(data) data |>
#         select(schoolid, childid) |>
#         summarize(schools = length(unique(schoolid)),
#                   students = length(unique(childid)))) |>
#   list_rbind() |>
#   summarize(across(everything(), \(value)
#                    range(value) |> 
#                      reduce(`-`) |>
#                      abs())) |>
#   j_gt() |>
#   tab_header("Units Removed")

```

```{r ecls_info}
#| layout-ncol: 2
ecls_dat |>
  select(schoolid, childid) |>
  summarize(schools = length(unique(schoolid)),
            students = length(unique(childid))) |>
  j_gt() |>
  tab_header("Total Units Remaining")

ecls_dat |>
  select(schoolid, childid) |>
  summarize(.by = schoolid,
            n_students = length(unique(childid))) |>
  ggplot(aes(x = n_students, y = after_stat(density))) +
  geom_histogram(binwidth = 1, alpha = .8) +
  scale_y_continuous("Percent", labels = scales::label_percent()) +
  guides(y = guide_axis(cap = T),
         x = guide_axis("Students Per School", cap = T)) +
  theme(geom = element_geom(ink = "skyblue3", color = "skyblue3"))
```


Distributions of the outcome and predictors in the remaining data.

```{r ecls_distributions}
#| fig-height: 3
ecls_dat |>
  select(-c(childid, schoolid)) |>
  imap(\(var, name) ecls_dat |> 
         ggplot(aes(x = var)) +
         {if (length(unique(var)) == 2) geom_bar() else geom_histogram(bins = 14)} +
         {if (length(unique(var)) == 2) scale_x_continuous(breaks = unique(var)) else NULL} +
         guides(x = guide_axis(name, cap = "both"),
                y = guide_axis(cap = "both")) +
         theme(aspect.ratio = 1)) |>
         wrap_plots()
```

Results from the model applied to the full dataset.

::: {style="font-size:70%"}
```{r tab_models}
#| layout-ncol: 2
m0 <- tar_read(full_unconditional_model, here::here("_targets"))
sjPlot::tab_model(m0,
                  title = "Unconditional")

m1 <- tar_read(full_conditional_model, here::here("_targets"))
sjPlot::tab_model(m1,
                  title = "Conditional")
```
:::


## Bootstrapping

```{r param_tbl}
#| column: margin
tibble(parameters = names(param_set),
       values = map(param_set, \(values) reduce(values, list))) |>
  gt() |>
  tab_style(cell_text(weight = "bold"),
            cells_column_labels()) |>
  cols_label_with(fn = str_to_title)

n_conditions <- param_set |> map(length) |> reduce(`*`)
```

Starting conditions: number of level-one units (students) within level-two units (schools). This set of parameters creates `r n_conditions` conditions.

```{r condition_plts}
#| column: page
#| fig-height: 8
#| layout-ncol: 2
#| warning: false
targets::tar_read(condition_plt_files, 
                  store = here::here("_targets")) |>
  unlist() |>
  knitr::include_graphics()
```


#### Other Distributions by Condition

::: panel-tabset

### ICC

```{r icc_plt}
icc_plt
```

### $R^2$ 

```{r r2_plt}
r2_plt
```

:::


<!-- ## Bootstrapping From One Subset -->

<!-- ```{r condition_plts_v_subset} -->
<!-- #| column: page -->
<!-- #| fig-height: 8 -->
<!-- #| layout-ncol: 2 -->
<!-- #| warning: false -->

<!-- targets::tar_read(condition_plt_v_subset_files,  -->
<!--                   store = here::here("_targets")) |> -->
<!--   unlist() |> -->
<!--   knitr::include_graphics() -->
<!-- ``` -->


## Simulated Data from Bootstrap Hit

```{r examples_params_tbl}
examples_params |>
  select(-iter) |>
  unique() |>
  group_split(.by = example_type,
              .keep = F) |>
  map(\(data) {
    title <- data$example_type
    data |>
      select(-example_type) |>
      pivot_longer(everything(),
                   names_to = "Parameter",
                   values_to = "Value") |>
      j_gt() |>
      fmt_number() |>
      tab_header(title = str_to_title(title))
    } |> wrap_table()) |>
  wrap_plots(ncol = 2)
```

```{r examples_spaghetti_plts}
#| layout-ncol: 2
#| fig-height: 2.5
walk(examples_spaghetti_plts, print)
```


```{r examples_condition_plts}
#| column: page
#| layout-ncol: 2
targets::tar_read(examples_condition_plt_files, 
                  store = here::here("_targets")) |>
  unlist() |>
  knitr::include_graphics()
```

::: panel-tabset

### ICC

```{r examples_icc_plt}
examples_icc_plt
```

### $R^2$ 

```{r examples_r2_plt}
examples_r2_plt
```

:::

<!-- ## Generated Data -->

<!-- Generating data from model estimates of one bootstrap hit. -->

<!-- ```{r} -->
<!-- # bs_dat |> -->
<!-- #   pluck(1) |> -->
<!-- #   unnest(tidy) |> -->
<!-- #   filter(term == "ses") |> -->
<!-- #   filter(estimate > quantile(estimate, .97)) |> -->
<!-- #   arrange(desc(estimate)) # didn't estimate intercept -->

<!-- bs_dat |> -->
<!--   pluck(1) |> -->
<!--   unnest(tidy) |> -->
<!--   filter(term == "sd__(Intercept)") |> -->
<!--   filter(estimate > quantile(estimate, .97)) |> -->
<!--   arrange(desc(estimate)) -->

<!-- data_gen_params <- bs_dat |> -->
<!--   pluck(1) |> -->
<!--   filter(id == "331") |> -->
  <!-- unnest(tidy) |> -->
  <!-- select(param_n_bootstraps, param_n_schools, param_n_students, term, estimate) |> -->
  <!-- pivot_wider(names_from = term, values_from = estimate) -->

<!-- data_gen_params |> -->
<!--   gt() |> -->
<!--   fmt_number() -->

<!-- data_gen_vcov <- matrix(c(data_gen_params$`sd__(Intercept)`, -->
<!--          0, -->
<!--          0, -->
<!--          data_gen_params$`sd__ses`), -->
<!--        ncol = 2, byrow = T) %*% -->
<!--   matrix(c(1, -->
<!--            data_gen_params$`cor__(Intercept).ses`, -->
<!--            data_gen_params$`cor__(Intercept).ses`, -->
<!--            1), -->
<!--        ncol = 2, byrow = T) %*% -->
<!--   matrix(c(data_gen_params$`sd__(Intercept)`, -->
<!--            0, -->
<!--            0, -->
<!--            data_gen_params$`sd__ses`), -->
<!--        ncol = 2, byrow = T) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- gen_data <- function(data_gen_params) { -->
<!--   tibble(schoolid = seq(1, data_gen_params$param_n_schools), -->
<!--          n_students = data_gen_params$param_n_students, -->
<!--          private = rbinom(data_gen_params$param_n_schools, 1, .3), -->
<!--          beta_ses = data_gen_params$ses, -->
<!--          beta_private = data_gen_params$private, -->
<!--          beta_private_by_ses = data_gen_params$`ses:private`) |> -->
<!--     bind_cols(varying_effects = MASS::mvrnorm(data_gen_params$param_n_schools, -->
<!--                                               mu = c(data_gen_params$`(Intercept)`, data_gen_params$ses), -->
<!--                                               Sigma = data_gen_vcov) |> -->
<!--                 as_tibble() |> -->
<!--                 set_names(c("alpha_school", "beta_ses_school"))) |> -->
<!--     uncount(n_students) |> -->
<!--     mutate(studentid = row_number(), -->
<!--            .after = schoolid) |> -->
<!--     mutate(ses = rnorm(data_gen_params$param_n_schools * data_gen_params$param_n_students), -->
<!--            private_by_ses = private * ses, -->
<!--            mu_school = alpha_school + -->
<!--              beta_private * private + -->
<!--              beta_private_by_ses * private_by_ses, -->
<!--            mu = mu_school + beta_ses * ses, -->
<!--            mathscore = rnorm(data_gen_params$param_n_schools * data_gen_params$param_n_students, -->
<!--                         mean = mu, sd = data_gen_params$sd__Observation)) |> -->
<!--     nest(gen_params = c(starts_with("beta"), starts_with("alpha"), starts_with("mu"))) -->
<!-- } -->


<!-- ``` -->

<!-- ```{r} -->
<!-- #| warning: false -->
<!-- #| message: false -->
<!-- frm <- mathscore ~ ses * private + (ses | schoolid) -->

<!-- bs_gen_dat <- tibble(iter = seq(1, data_gen_params$param_n_bootstraps), -->
<!--                      strap = map(iter, \(iter) gen_data(data_gen_params))) |> -->
<!--   mutate(res = map(strap,  -->
<!--                    safely(\(strap) lme4::lmer(frm, -->
<!--                                               data = strap), -->
<!--                           otherwise = NA_real_)), -->
<!--          model = map(res, "result"), -->
<!--          error = map_chr(res, \(res) pluck(res, "error", "message", .default = NA)), -->
<!--          tidy = imap(model, \(model, idx) model |> -->
<!--                        broom.mixed::tidy() |> -->
<!--                        mutate(iter = idx)), -->
<!--          opt_warnings = map_chr(model, get_warnings), -->
<!--          lme4_warnings = map_chr(model, get_lme4_warnings)) |> -->
<!--   bind_cols(data_gen_params) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| column: page -->
<!-- #| fig-height: 8 -->
<!-- #| warning: false -->

<!-- list(bs_gen_dat) |> -->
<!--   walk(\(bootres) { -->
<!--     plt_dat <- make_plt_dat(bootres) -->

<!--     pat <- make_plt_pattern(plt_dat) -->

<!--     n_terms <- plt_dat |> -->
<!--       select(n_terms) |> -->
<!--       max() -->

<!--     table_height_prop <- 1/4 -->

<!--     { -->
<!--       (plt_dat |> -->
<!--          pull(plots) |> -->
<!--          unlist(recursive = F) |> -->
<!--          append(wrap_table(make_warnings_tbl(bootres))) |> -->
<!--          wrap_plots(design = pat, -->
<!--                     axes = "collect", -->
<!--                     heights = c(rep(((1 - table_height_prop) / n_terms),  -->
<!--                                   times = n_terms), -->
<!--                                 table_height_prop))) |> -->
<!--         cowplot::ggdraw() +  -->
<!--         cowplot::draw_label( -->
<!--           plot_annotation("Generated Data Bootstrap"), -->
<!--           x = 0.5, y = 1, vjust = 1, fontface = "bold", size = 14) -->
<!--     } |> -->
<!--       print() -->
<!--   }) -->
<!-- ``` -->

<!-- #### Other Distributions by Condition -->

<!-- ::: panel-tabset -->

<!-- ### ICC -->

<!-- ```{r} -->
<!-- #| message: false -->
<!-- #| warning: false -->
<!-- icc_dat <- list(bs_gen_dat) |> -->
<!--   map(\(data) data |> -->
<!--         select(model) |> -->
<!--         mutate( -->
<!--           icc = map_dbl(model, \(model) { -->

<!--             icc <- performance::icc(model) |> -->
<!--               pluck("ICC_adjusted")  -->

<!--             ifelse(is.null(icc), NA, icc)   -->
<!--           }) -->
<!--         )) -->


<!-- icc_dat |> -->
<!--   map(\(data) data |> -->
<!--         ggplot(aes(x = icc)) + -->
<!--         geom_density(na.rm = T) + -->
<!--         geom_text(data = data |> -->
<!--                     mutate(icc_error = is.na(icc)) |> -->
<!--                     summarize(percent_removed = mean(icc_error) * 100), -->
<!--                   aes(label = glue::glue("{round(percent_removed, 2)}% ICCs errored"), -->
<!--                       x = -Inf, y = Inf, vjust = 1, hjust = 0)) + -->
<!--         scale_x_continuous("ICC", limits = c(0, 1), breaks = seq(0, 1, .2)) + -->
<!--         scale_y_continuous(NULL, breaks = NULL) + -->
<!--         guides(x = guide_axis(cap = T)) + -->
<!--         theme(aspect.ratio = (1.618)^-1, -->
<!--               axis.line.y = element_blank())) |> -->
<!--   wrap_plots(ncol = 2, axes = "collect_x") -->
<!-- ``` -->

<!-- ### $R^2$ -->

<!-- ```{r} -->
<!-- #| message: false -->
<!-- #| warning: false -->
<!-- #| results: hide -->
<!-- r2_dat <- list(bs_gen_dat) |> -->
<!--   map(\(data) data |> -->
<!--         select(model) |> -->
<!--         mutate( -->
<!--           r2s = map(model, \(model) { -->

<!--             r2s <- performance::r2(model)  -->

<!--             r2_conditional <- r2s$R2_conditional -->
<!--             r2_marginal <- r2s$R2_marginal -->

<!--             tribble(~ r2_type, ~ r2_estimate, -->
<!--                     "conditional", ifelse(is.null(r2_conditional), NA, r2_conditional), -->
<!--                     "marginal", ifelse(is.null(r2_marginal), NA, r2_marginal)) -->
<!--           }) -->
<!--         ) |> -->
<!--             unnest(r2s)) -->


<!-- r2_dat |> -->
<!--   map(\(data) { -->
<!--     error_dat <- data |> -->
<!--       mutate(r2_error = is.na(r2_estimate)) |> -->
<!--       summarize(.by = r2_type, -->
<!--                 percent_removed = mean(r2_error) * 100) |> -->
<!--       mutate(string = glue::glue("{round(percent_removed, 2)}% {r2_type} R^2s errored")) -->

<!--     data |> -->
<!--       ggplot(aes(x = r2_estimate, color = r2_type)) + -->
<!--       geom_density(na.rm = T) + -->
<!--       geom_text(data = error_dat, -->
<!--                 aes(label = string, -->
<!--                     x = -Inf, y = Inf, vjust = c(1, 2.3), hjust = 0)) + -->
<!--       scale_x_continuous("R^2", limits = c(0, 1), breaks = seq(0, 1, .2)) + -->
<!--       scale_y_continuous(NULL, breaks = NULL) + -->
<!--       guides(x = guide_axis(cap = T), -->
<!--              color = guide_none()) + -->
<!--       theme(aspect.ratio = (1.618)^-1, -->
<!--             axis.line.y = element_blank(), -->
<!--             axis.title.x = ggtext::element_markdown()) -->
<!--     }) |> -->
<!--  wrap_plots(ncol = 2, axes = "collect_x") -->
<!-- ``` -->

## Archive

<!-- ```{r} -->
<!-- bootstr <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") -->

<!-- t1 <- Sys.time() -->
<!-- bootres <- bootstr |> -->
<!--   mutate(model = map(strap,  -->
<!--                      \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                          data = strap)), -->
<!--          tidy = map(model, broom.mixed::tidy), -->
<!--          opt_warnings = map_chr(model, get_warnings), -->
<!--          lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- t2 <- Sys.time() -->

<!-- get_bootres <- function(bootstrapped_dat) { -->
<!--   frm <- mathscore ~ ses * private + (ses | schoolid) -->

<!--   bootstrapped_dat |> -->
<!--     mutate(model = map(strap,  -->
<!--                        \(strap) lme4::lmer(frm, -->
<!--                                            data = strap)), -->
<!--            tidy = map(model, broom.mixed::tidy), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- } -->

<!-- t3 <- Sys.time() -->
<!-- get_bootres(bootstr) -->
<!-- t4 <- Sys.time() -->

<!-- (t2 - t1) -->
<!-- (t4 - t3) -->

<!-- bootest <- bootres |> -->
<!--   # giving each `tidy` an iteration id -->
<!--   mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) |> -->
<!--   list_rbind() |> -->
<!--   select(group, term, estimate, iter) -->
<!-- ``` -->



<!-- ```{r} -->
<!-- bootstr <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") -->

<!-- t1 <- Sys.time() -->
<!-- bootres <- ecls_dat |> -->
<!--   # should this take into account the clustering more? -->
<!--   modelr::bootstrap(n_bootstraps, id = "id") |> -->
<!--   mutate(model = map(strap,  -->
<!--                      \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                          data = strap)), -->
<!--          tidy = map(model, broom.mixed::tidy), -->
<!--          opt_warnings = map_chr(model, get_warnings), -->
<!--          lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- t2 <- Sys.time() -->

<!-- get_bootres <- function(n_bootstraps) { -->
<!--   frm <- mathscore ~ ses * private + (ses | schoolid) -->

<!--   ecls_dat |> -->
<!--     # should this take into account the clustering more? -->
<!--     modelr::bootstrap(n_bootstraps, id = "id") |> -->
<!--     mutate(model = map(strap,  -->
<!--                        \(strap) lme4::lmer(frm, -->
<!--                                            data = strap)), -->
<!--            tidy = imap(model, \(model, idx) model |> -->
<!--                         broom.mixed::tidy() |> -->
<!--                         mutate(iter = idx)), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!-- } -->

<!-- t3 <- Sys.time() -->
<!-- get_bootres(n_bootstraps) -->
<!-- t4 <- Sys.time() -->

<!-- (t2 - t1) -->
<!-- (t4 - t3) -->

<!-- b <- get_bootres(10) -->

<!-- b |> mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) -->

<!-- bootest <- bootres |> -->
<!--   # giving each `tidy` an iteration id -->
<!--   mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--   pull(tidy) |> -->
<!--   list_rbind() |> -->
<!--   select(group, term, estimate, iter) -->
<!-- ``` -->




<!-- ```{r} -->

<!-- plt_dat <- tibble(term = terms) |> -->
<!--   mutate(plot_terms = imap(term, \(term, idx) tibble(xterm = term, -->
<!--                                                      yterm = head(terms, idx))), -->
<!--          n_terms = map_int(plot_terms, \(plot_terms) nrow(plot_terms)), -->
<!--          n_prev_terms = map_int(n_terms, \(n_terms) seq(n_terms - 1, 0) |> sum()), -->
<!--          # pat only worked as a way to setup the patchwork when length(terms) < 7 -->
<!--          pat = map2_chr(n_terms, n_prev_terms, -->
<!--                         \(n_terms, n_prev_terms) paste0(LETTERS[seq(n_prev_terms + 1, length.out = n_terms)] |>  -->
<!--                                                           paste(collapse = ""), -->
<!--                                             rep("#", times = length(terms) - n_terms) |> paste(collapse = "")))) |> -->
<!--   mutate(plots = map(plot_terms, -->
<!--                           \(plot_terms) plot_terms |> -->
<!--                             mutate(plot = map2(xterm, yterm, -->
<!--                                                \(xterm, yterm) { -->

<!--                                                  df <- bootest |> -->
<!--                                                    filter(term %in% c(xterm, yterm)) |> -->
<!--                                                    select(term, estimate, iter) |> -->
<!--                                                    pivot_wider(names_from = term, values_from = estimate) -->

<!--                                                  mapping <- if (xterm == yterm) { -->
<!--                                                    do.call(aes, list(x = as.name(xterm))) -->
<!--                                                  } else { -->
<!--                                                    do.call(aes, list(y = as.name(xterm), x = as.name(yterm))) -->
<!--                                                  } -->
<!--                                                  geom <- if (xterm == yterm) geom_density() else geom_point() -->

<!--                                                  ggplot(df, mapping) +  -->
<!--                                                    geom + -->
<!--                                                    {if (xterm == yterm) labs(y = NULL) else NULL} + -->
<!--                                                    scale_x_continuous(breaks = NULL) + -->
<!--                                                    scale_y_continuous(breaks = NULL) + -->
<!--                                                    theme_classic() -->
<!--                                                }))  |> pluck("plot"))) -->


<!-- ``` -->
```{r}
#| eval: false



# bootres <- get_bootres(10)
# 
# plt_dat <- make_plt_dat(bootres)
# 
# pat <- make_plt_pattern(plt_dat)
# 
# plt_dat |>
#     pull(plots) |>
#     unlist(recursive = F) |>
#     wrap_plots(design = pat,
#                axes = "collect")

list(n_bootstraps = c(10, 20),
     n_students = c(3, 10),
     n_schools = c(5, 20)) |>
  do.call(crossing, args = _) |>
  mutate(condition_id = row_number()) |>
  nest(params = -condition_id) |>
  pull(params) |>
  map(\(params) {
    print(params)
    
    params |>
      pivot_longer(everything(),
                   names_to = "param",
                   values_to = "value") |>
      pmap(\(param, value) assign(param, value))
    
    glue::glue("{param}: {value}")
  })

# bs_dat <- do.call(crossing, params) |>
#   mutate(condition_id = row_number()) |>
#   pmap(\(...) {
#     list2env(list(...), envir = environment())
#     glue::glue("condition {condition_id}: n_bootstraps={n_bootstraps}, n_students={n_students}, n_schools={n_schools}")
#     
#     get_bootres(n_bootstraps, n_students, n_schools) |>
#       mutate(condition_str = glue::glue("condition {condition_id}: n_bootstraps={n_bootstraps}, n_students={n_students},  n_schools={n_schools}"))
#   })



bs_dat |>
  head(2) |>
  map(\(bootres) {
    plt_dat <- 
    
    make_plt_pattern(plt_dat)
    })

make_plt_dat(bres) |>
    get_table_row_location

p1 <- ggplot(mtcars) + geom_point(aes(mpg, disp)) + theme_classic()
p2 <- ggplot(mtcars) + geom_boxplot(aes(gear, disp, group = gear)) + theme_classic()
p3 <- ggplot(mtcars) + geom_bar(aes(gear)) + facet_wrap(~cyl) + theme_classic()


design <- "
  AB
  AC
"

(p1 + p2 + p3) +
  plot_layout(design = design, heights = c(3, 1), axes = "collect") &
  theme_classic()
```

<!-- ### Bootstrapped Data -->

<!-- ```{r} -->
<!-- m1_bs <- function(n_students) { -->
<!--   bootstr <- ecls_dat |> -->
<!--     filter(.by = schoolid, -->
<!--            childid %in% sample(childid, n_students)) |> -->
<!--     modelr::bootstrap(n_bootstraps, id = "studentid") -->

<!--   bootres <- bootstr |> -->
<!--     mutate(model = map(strap, -->
<!--                        \(strap) lme4::lmer(mathscore ~ ses * private + (ses | schoolid), -->
<!--                                            dat = strap)), -->
<!--            tidy = map(model, broom.mixed::tidy), -->
<!--            opt_warnings = map_chr(model, get_warnings), -->
<!--            lme4_warnings = map_chr(model, get_lme4_warnings)) -->
<!--   #  -->
<!--   # # n_students <- bootres |> -->
<!--   # #   pull(n_students) |>  -->
<!--   # #   first() -->
<!--   #  -->
<!--   bootest <- bootres |> -->
<!--     # giving each `tidy` an iteration id -->
<!--     mutate(tidy = imap(tidy, \(tidy, idx) mutate(tidy, iter = idx))) |> -->
<!--     pull(tidy) |> -->
<!--     list_rbind() |> -->
<!--     select(group, term, estimate, iter) -->
<!--   #  -->
<!--   terms <- bootest |> pull(term) |> unique() -->

<!--   plt_dat <- tibble(term = terms) |> -->
<!--     mutate(plot_terms = imap(term, \(term, idx) tibble(xterm = term, -->
<!--                                                        yterm = head(terms, idx))), -->
<!--            n_terms = map_int(plot_terms, \(plot_terms) nrow(plot_terms)), -->
<!--            n_prev_terms = map_int(n_terms, \(n_terms) seq(n_terms - 1, 0) |> sum()), -->
<!--            pat = map2_chr(n_terms, n_prev_terms, -->
<!--                           \(n_terms, n_prev_terms) paste0(LETTERS[seq(n_prev_terms + 1, length.out = n_terms)] |> -->
<!--                                                             paste(collapse = ""), -->
<!--                                                           rep("#", times = length(terms) - n_terms) |> paste(collapse = "")))) |> -->
<!--     mutate(plots = map(plot_terms, -->
<!--                        \(plot_terms) plot_terms |> -->
<!--                          mutate(plot = map2(xterm, yterm, -->
<!--                                             \(xterm, yterm) { -->

<!--                                               df <- bootest |> -->
<!--                                                 filter(term %in% c(xterm, yterm)) |> -->
<!--                                                 select(term, estimate, iter) |> -->
<!--                                                 pivot_wider(names_from = term, values_from = estimate) -->

<!--                                               mapping <- if (xterm == yterm) { -->
<!--                                                 do.call(aes, list(x = as.name(xterm))) -->
<!--                                               } else { -->
<!--                                                 do.call(aes, list(y = as.name(xterm), x = as.name(yterm))) -->
<!--                                               } -->
<!--                                               geom <- if (xterm == yterm) geom_density() else geom_point() -->

<!--                                               ggplot(df, mapping) + -->
<!--                                                 geom + -->
<!--                                                 {if (xterm == yterm) labs(y = NULL) else NULL} + -->
<!--                                                 scale_x_continuous(breaks = NULL) + -->
<!--                                                 scale_y_continuous(breaks = NULL) + -->
<!--                                                 theme_classic() -->
<!--                                             }))  |> pluck("plot"))) -->


<!--   pat <- plt_dat |> -->
<!--     select(n_terms, n_prev_terms) |> -->
<!--     mutate(areas = map(n_terms, -->
<!--                        \(n_terms) seq(1, n_terms) |> -->
<!--                          map2(n_terms, \(y, x) c(x, y)) -->
<!--     )) |> -->
<!--     pull(areas) |> -->
<!--     list_flatten() |> -->
<!--     map(\(a) area(t = a[1], l = a[2], b = a[1], r = a[2])) |> -->
<!--     reduce(c) -->


<!--   plt_dat |> -->
<!--     pull(plots) |> -->
<!--     unlist(recursive = F) |> -->
<!--     wrap_plots(design = pat, -->
<!--                axes = "collect") + -->
<!--     plot_annotation(title = glue::glue("Students per Classroom: {n_students}")) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- list(3, 10) |> -->
<!--   map(\(n_students) m1_bs(n_students)) -->


<!-- bootres <- list(3, 10) |> -->
<!--   map(\(n_students) m1_bs(n_students)) -->

<!-- m1_bs(3) -->

<!-- bootres |> -->
<!--   map(m1_bs_plt) -->

<!-- bootres |> -->
<!--   map(\(bootres) bootres |> -->
<!--         summarize(opt_warnings = list(unique(opt_warnings)))) -->
<!-- ``` -->











